\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-09 related-work.tex
blume et al.

\citet{bac2006} address the expression problem in a functional setting,
introducing a language mechanism that allows pattern-matching cases to
be added retroactively in accordance with extensions to variant types.
Our \lsti{FRecursion} and \lsti{FInduction} commands achieve a similar
functionality, with families bestowing additional organizational power.

>>>>

\citet{bac2006} address the expression problem for a core subset of Standard~ML
by combining explicitly coded open recursion with a mechanism that
allows pattern-matching cases to be defined separately and combined
later.
Our \lsti{FRecursion} and \lsti{FInduction} commands achieve a similar
functionality, with families making open recursion implicit and
bestowing organizational power.
